\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
% PDF setup 
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
  %\usepackage[hidelinks]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\usepackage{changepage}
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
%\newcommand{\resheading}[1]{{\small\colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1\vphantom{p&%\^E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{\huge {Priyanka Nath}} \\\\
\indent 6/83 Bijoygarh, Jadavpur, \\
\indent Kolkata -- 700032, India.\\
\indent {email:} \href{mailto: pnath.it@gmail.com}{\textbf{pnath.it@gmail.com}} \\
\indent mobile: \textbf{+91 990 321 5630} \\

%\resheading{\textbf{Objective} }\\\\[\lsep]
%
%\begin{adjustwidth}{15pt}{0pt}
%Seeking a summer internship in computer science as an opportunity to learn how to undertake research and enhance my skills \& knowledge.\\
%\end{adjustwidth}


\resheading{\textbf{Education} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{KIIT University }\textit{(formerly Kalinga Institute Of Industrial Technology) \textbf{--}}
Bhubaneshwar, India & \small{\emph{July, 2015 - Present}}\\
\emph{Bachelor of Technology, Information Technology} & \small{\emph{Current GPA: 8.75 / 10.0}}\\
\end{tabular*}\\\\

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{South Point High School --} Kolkata, India\\[0.1cm]
{All India Senior School Certificate Examination, {\scriptsize \textbf{CBSE}} (Grade 12)} & \small{\emph{June, 2015}} \\
%{June, 2015 - 76.2\%}}
\emph{Stream: Science with Computer Science as additional subject}\\[0.15cm]
{Secondary Examination, {\scriptsize \textbf{WBBSE}} (Grade 10)} & \small{\emph{May, 2013}} \\\\
%{May, 2013 - 87.42\%}}
\end{tabular*}

\resheading{\textbf{Publications} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\emph{Priyanka Nath}, Sumran Kilam, Aleena Swetapadma. \textbf{'A machine learning approach to predict volatile}\\
\textbf{substance abuse for drug risk analysis'}. 2017, \emph{Third IEEE International Conference on Research in}\\ \emph{Computational
Intelligence and Communication Networks (ICRCICN 2017)}. Published in IEEE Xplore. 
\\
\end{tabular*}\\\\

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Divya Kumari, Sumran Kilam, \emph{Priyanka Nath},  Aleena Swetapadma, \textbf{'Prediction of alcohol abused}\\\textbf{individuals using artificial neural network'. 2018, \emph{14\textsuperscript{th} International Conference on Distributed Computing and} \\\emph{Internet Technology (ICDCIT 2018)}. Published by Springer.
\\
\end{tabular*}\\\\

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Divya Kumari, \emph{Priyanka Nath}, Sumran Kilam, Aleena Swetapadma, \textbf{'Volatile Substance Abuse: A Nearest}\\\textbf{Neighbor Based Analysis'}. 2018, \emph{International Conference on Innovative Technologies in Engineering
(ICITE 2018)}.
\\
\end{tabular*}\\\\

\resheading{\textbf{Experience} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Indian Statistical Institute – } Kolkata, India
\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\small{\emph{      May, 2018 - July, 2018}}\\
\emph{Advisor - Prof. Bimal Kumar Roy}\\
{Research Intern at R. C. Bose Centre for Cryptology and Security, Indian Statistical Institute}\\\\

\textbf{Indian Statistical Institute – } Kolkata, India
\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\small{\emph{      May, 2017 - July, 2017}}\\
\emph{Advisor - Prof. Ansuman Banerjee}\\
{Research Intern under the \emph{Summer Internship Program in Cryptology 2017}, R. C. Bose Centre for Cryptology}\\
{and Security, Indian Statistical Institute (funded by Microsoft Research India).}\\

\end{tabular*}\\\\

\resheading{\textbf{Projects} }\\\\[\lsep]
%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

\\\indent\textbf{Bias Verification Of Riverst Cipher - 4 Keystream - }Indian Statistical Institute, \small{\emph{May, 2017 - July, 2017}}\\
\indent{- Created a sample set of 10,000,000 cipher texts using randomly generated keys of 128 bit}
\\\indent{- Calculated the probability of each byte in the cipher text to be a certain number from 0 to 255}\\\indent{- Plotted the data to verify that the RC-4 keystream is biased}\\

\\\indent\textbf{Artificial Neural Networks Implementation On The Game 'Snake!'}\\
\indent{- Created the game Snake from scratch in Python}\\\indent{- Extracted features by generating random moves}\\\indent{- Used the extracted features to classify if a move is valid or invalid using Artificial Neural Networks}\\


\\\indent\textbf{Linux System Call Analysis – } Indian Statistical Institute,
\small{\emph{May, 2017 - July, 2017}}\\
\indent{- Developed an OS system call pattern matching \& analysis application for Linux to detect software vulnerabilities.}\\
\indent{- Using inputs generated by an automated fuzzer, American Fuzzy Lop (AFL), to detect malicious binaries.}\\
\indent{- Summer internship project, funded by the Defence Research and Development Organisation (DRDO),}\\ \indent{Government of India.}\\

\indent\textbf{Volatile Substance Abuse (VSA) Drug Risk Analysis}\\
\indent{- Built an Artificial Neural Networks model using Lavenberg Marquardt algorithm in Matlab to predict VSA }\\\indent{use of individuals based on their five factor personality model, demography, etc.}\\

\indent\textbf{\href{https://github.com/p-nath/pca_cuda}{Principal Component Analysis using GPUs}}\\
\indent{- Implemented dimensionality reduction by applying PCA on Fischer's Iris dataset using CUDA-C.}\\

\indent\textbf{\href{https://github.com/p-nath/bookmarkz}{Bookmarkz: A Social Bookmarking App}}\\
\indent{- Developed a social bookmarking app using Django web framework where a user can create an account,}\\ 
\indent{share bookmarks, vote on shared bookmarks, etc.}\\% \emph{{\href{https://mybookmarkz.herokuapp.com/}{[https://mybookmarkz.herokuapp.com/]}}}\\

\indent\textbf{Vigenère Decoder and Rivest Cipher Implementations}\\
\indent{- Built a \href{https://github.com/p-nath/VigenereCipherCrack}{Vigenère Cipher Decoder} which predicts 5 probable keywords given the encrypted
ciphertext.}\\
\indent{- Implemented a \href{https://github.com/p-nath/rc4}{Rivest Cipher 4 (RC4)} in Python and showed that the keystream generated by the RC4}\\\indent{is biased is varying degrees towards certain sequences.}\\


\indent\textbf{Naive Bayes Classifier }\\
\indent{- Implemented a Naive Bayes Classifier from scratch for handwritten digits from MNIST digit dataset.}\\

\indent\textbf{SpaceTurtle: An Introduction to  Turtle Programming}\\
\indent{- Designed a teaching kit for a Mozilla Hackathon, using Python's turtle library, to introduce kids to} \\
\indent{programming and encourage them to solve problems through logical thinking.}\\

\indent\textbf{MysticSquare: An Android Game}\\
\indent{- Made a basic Mystic-Square (also known as 15 puzzle) game for Android using Android Studio.}\\\\
%\end{tabular*}

\resheading{\textbf{Technical Skills} }\\\\[\lsep]

\indent\textbf{Programming -- }Coded mainly in \textbf{C, Python.} Proficient in coding with C++ and Java.\\
\indent\textbf{Web -- } HTML, CSS, Javascript. \indent\indent\textbf{OS -- } Linux, Windows.\\
\indent\textbf{Development Tools --} Android Studio, Android SDK, SQL (MySQL, Oracle), scikit, Matlab, Latex.\\\\


\resheading{\textbf{Relevant Courses Taken} }\\\\[\lsep]

\indent Linear Algebra, Data Structures \& Algorithms, Object Oriented Programming, Probability \& Statistics,\\
\indent Discrete Mathematics, Computer Networking, Operating Systems, Database Management Systems.\\
\indent\textbf{MOOCs -- }Machine Learning (by Andrew Ng), Cryptography I (by Dan Boneh).\\
\\


\resheading{\textbf{Honors \& Achievements}}\\[\lsep]\\[-0.2cm]
\begin{itemize}

\item {Secured 4\textsuperscript{th} position among 11,000 participants in the 4th CSI National Programming Contest organised by the Computer Society Of India.}
\item {Won 2\textsuperscript{nd} place in HelloWeb Hackathon 2016 hosted by the MozillaBBSR Club by designing a teaching kit to introduce kids to programming.}
%\item {Qualified for Round 1 of the Facebook HackerCup 2017.}
\item {Secured the highest grade "O" in Object Oriented Programming, Web Technology and Computer Networks as part of my B.Tech curriculum. }
\item {Secured a perfect score (100\%) in Mathematics in state-wide Secondary Examination, 2013 among 1,020,000 students.}
\item {Awarded Chitroprobha Upadhi Certification by Bengal Music College, Kolkata, India in 2012 on completing a 6--year course on Painting.}
\item {Selected as one of 20 student judges from MP Birla group of schools for the cultural committee MP Birla Puja Utkarsh Samman 2014.}
\end{itemize}


\end{document}

