\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
% PDF setup 
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
  %\usepackage[hidelinks]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\usepackage{changepage}
%\usepackage[top=0.5in, bottom=0.5in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}

\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\usepackage[bindingoffset=0.2in,%
            left=0.2in,right=0.8in,top=0.5in,bottom=0.5in]{geometry}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
%\newcommand{\resheading}[1]{{\small\colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1\vphantom{p&%\^E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.5in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
%\hspace{0.5cm}\\[-0.2cm]

{\begin{center}
{\textbf{\huge {Priyanka Nath}} \\[0.25cm]
\indent 700 Health Sciences Dr., Chapin-L-2175B, Stony Brook, NY-- 11790, India | \emph{cell:} {+1.805.722.6207}\\
\indent {\emph{email:}} \href{mailto: pnath.it@gmail.com}{\textbf{pnath.it@gmail.com}} | \emph{website:} \href{https://p-nath.github.io/}{https://p-nath.github.io/}\\}
\end{center}}


%\resheading{\textbf{Objective} }\\\\[\lsep]
%
%\begin{adjustwidth}{15pt}{0pt}
%Seeking a summer internship in computer science as an opportunity to learn how to undertake research and enhance my skills \& knowledge.\\
%\end{adjustwidth}


\resheading{\textbf{Education} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Stony Brook University }\textit{(SUNY Stony Brook) \textbf{--}}
NewYork, USA & \small{\emph{August, 2019 - Present}}\\
\emph{Master of Science (Computer Science)} & \small%{\emph{Current GPA: 8.79 / 10.0}}\\
\end{tabular*}\\\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{KIIT University }\textit{(formerly Kalinga Institute Of Industrial Technology) \textbf{--}}
Bhubaneshwar, India & \small{\emph{July, 2019 - 8.79 / 10.0}}\\
\emph{Bachelor of Technology, Information Technology} \\
\end{tabular*}\\\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{South Point High School --} Kolkata, India\\\\[-0.1in]
{Senior School Certification Examination, (Grade 12)} %& \small{\emph{June, 2015 - 76.2\%}}\\
%{\scriptsize \textbf{CBSE}} (Grade 12)} 

\emph{Stream: Science with Computer Science as additional subject}\\[0.15cm]
{Secondary Examination, (Grade 10)} %& \small{\emph{{May, 2013 - 87.42\%}}}\\\\[-0.25cm]
%{\scriptsize \textbf{WBBSE}} (Grade 10)} 

\end{tabular*}

\resheading{\textbf{Publications} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Kumari, Divya, Priyanka Nath, Sumran Kilam, and Aleena Swetapadma. \textbf{"Volatile Substance Abuse: A Nearest}\\\textbf{Neighbor Based Analysis."} In International Conference on Innovative Technologies in Engineering (ICITE), 2018.\\
\end{tabular*}\\\\[-0.1cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Kumari, Divya, Sumran Kilam, Priyanka Nath, and Aleena Swetapadma. \textbf{"Prediction of alcohol abused}\\ \textbf{individuals using artificial neural network."} International Journal of Information Technology 10, no. 2 (2018):\\ 233-237.
\\
\end{tabular*}\\\\[-0.1cm]

\indent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Nath, Priyanka, Sumran Kilam, and Aleena Swetapadma. \textbf{"A machine learning approach to predict volatile}\\\textbf{substance abuse for drug risk analysis."} In Research in Computational Intelligence and Communication \\Networks (ICRCICN), 2017 Third International Conference on, pp. 255-258. IEEE, 2017.\\
\end{tabular*}\\\\[-0.2cm]

\resheading{\textbf{Experience} }\\\\[\lsep]\\[-0.3cm]

\indent
\begin
{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Amazon Inc. – } Bengaluru, India
\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\small{\emph{   March, 2019 - August, 2019}}\\
{Software Development Engineer Intern, Amazon Elasticsearch Service, Amazon Web Services.}\\\\[-0.2cm]

\textbf{Indian Statistical Institute – } Kolkata, India
\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\small{\emph{      May, 2018 - July, 2018}}\\
\emph{Advisor - Prof. Bimal Kumar Roy}\\
{Research Intern at R. C. Bose Centre for Cryptology and Security, Indian Statistical Institute.}\\\\[-0.2cm]

\textbf{Indian Statistical Institute – } Kolkata, India
\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\indent\small{\emph{      May, 2017 - July, 2017}}\\
\emph{Advisor - Prof. Ansuman Banerjee}\\
{Research Intern under the \emph{Summer Internship Program in Cryptology 2017}, R. C. Bose Centre for Cryptology}\\
{and Security, Indian Statistical Institute (funded by Microsoft Research India).}\\
\end{tabular*}\\\\[-0.2cm]


\resheading{\textbf{Projects} }\\\\[\lsep]

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}\textbf{Generation of API-Level Metrics for Amazon Elasticsearch Service  - } Amazon.com, Inc.
& \small{\emph{March, 2019 - August 2019}}\\
\end{tabular*}
\indent{-  Investigated existing metrics and determined what new metrics should be generated. Carried out a comparative}\\\indent{ study in support of the proposed metrics, weighing scalability, cost and impact on performance.}\\
\indent{- Implemented code to generate 19 new API-level metrics for every version of Amazon Elasticsearch Service. \\\indent These will be used for the diagnosis and analysis of clusters and thus improve customer experience.}\\[-0.1cm]

\indent\textbf{Drug Risk Analysis}\\
\indent{- Applied supervised learning using Artificial Neural Networks(ANN) to classify an individual as a user or\\\indent non-user of VSA and alcohol, based on a five-factor personality model. Predicted alcohol users with accuracy\\\indent of 98.7\% and VSA users with accuracy of 81\%.}\\
\indent{- Experimented with the number of neurons and hidden layers to predict the last time of use of VSA users with\\\indent 71.9\% accuracy and alcohol users with a 49.1\% accuracy.}\\
\indent{- Increased the accuracy of time of VSA drug use prediction to 96.4\% by implementing k-Nearest neighbours\\\indent classification.}\\[-0.1cm]

\indent\textbf{\href{https://github.com/p-nath/pca_cuda}{Principal Component Analysis using GPUs}}\\
\indent{- Implemented dimensionality reduction by applying PCA on Fischer's Iris dataset using C.}\\
\indent{- Optimized the compute-intensive process by  parallelizing it in CUDA-C by using GPUs.}\\
\indent{- Applied k-means clustering using scikit to verify that the reduction in the number of features did not\\\indent compromise the information stored in the dataset.}\\[-0.1cm]

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}\textbf{Bias Verification Of \href{https://github.com/p-nath/rc4}{Rivest Cipher (RC-4)} Keystream - } Indian Statistical Institute
& \small{\emph{May, 2018 - July, 2018}}\\
\end{tabular*}
\indent{- Implemented a RC-4 cipher in Python and proved that the second byte of the keystream generated by the}\\\indent{ pseudorandom generator is biased towards zero with a probability, which is twice the expected value.}\\
\indent{- Created a sample dataset of 10,000,000 cipher texts using randomly generated 32 bit keys and computed the \\\indent probability distribution of each byte.}\\\indent{- Verified the bias in the keystream by doing a graph analysis. Plotted the data to verify the bias in the rest of the\\\indent keystream as per the works of Sengupta et al.}\\[-0.1cm]

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}\textbf{Vulnerability Analysis of Linux System Calls – } Indian Statistical Institute
& \small{\emph{May, 2017 - July, 2017}}\\
\end{tabular*}
\indent{- Developed an OS system call pattern matching \& analysis application for Linux to detect software}\\\indent{     vulnerabilities.}\\
\indent{- Using inputs generated by an automated fuzzer, American Fuzzy Lop (AFL), to detect malicious binaries.}\\
\indent{- Summer internship project, funded by the Defence Research and Development Organisation (DRDO),}\\ \indent{Government of India.}\\[-0.1cm]

\indent\textbf{Artificial Neural Networks Implementation On The Game "Snake!"}\\
\indent{- Developed a popular video arcade game "Snake!" using the PyGame library.}\\\indent{- Extracted features by generating random moves and recording their results in the game, whether they were\\\indent favourable or not.}\\\indent{- Trained two models Artificial Neural Network through supervised learning to predict moves for optimal \\\indent scoring and survival of the snake.}\\[-0.1cm]

%\indent\textbf{\href{https://github.com/p-nath/bookmarkz}{Bookmarkz: A Social Bookmarking App}}\\
%\indent{- Developed a social bookmarking web application using Django framework, hosted on Heroku where an user}\\ 
%\indent { can create an account, share bookmarks, vote on shared bookmarks, interact through comments, etc.}\\[-0.1cm]

%\indent\textbf{\href{https://github.com/p-nath/VigenereCipherCrack}{Vigenère Cipher Decoder}}\\
%\indent{- Built a Vigenère Cipher Decoder which can solve for unknown Vigenère Cipher keys and then decrypt \\\indent encrypted cipher text encrypted using a predicted key.}\\
%\indent{- Applied cryptanalysis techniques (Kasiki Analysis) to predict key-lengths. Using the predicted key-lengths \\\indent along with the frequency  distribution data of letters in the alphabet, 5 probable keys are evaluated for decryption.}\\[-0.1cm]

\indent\textbf{Naive Bayes Classifier }\\
\indent{- Implemented a Naive Bayes Classifier from scratch for handwritten digits using Python.}\\
\indent{- Tested classifier on the MNIST handwritten digit dataset to have an accuracy of 64.3\%.}\\[-0.1cm]

\indent\textbf{SpaceTurtle: An Introduction to  Turtle Programming}\\
\indent{- Designed a teaching kit comprising simple interactive games to introduce kids to programming and \\ \indent encourage them to solve problems through logical thinking.}\\
\indent {- Won second prize in the Mozilla Hello Web hackathon, sponsored by Rotary International in association\\\indent with the Mozilla Learning initiative.}\\[-0.1cm]


\resheading{\textbf{Technical Skills} }\\\\[\lsep]

\indent\textbf{Programming -- }Coded mainly in \textbf{C, Python.} Proficient in coding with C++ and Java.\\
\indent\textbf{Web -- } HTML, CSS, JavaScript. \indent\indent\textbf{OS -- } Linux, Windows.\indent\indent\textbf{Machine Learning Tools --} scikit, Matlab, R.\\
\indent\textbf{Development Tools --} Android Studio, Android SDK, SQL (MySQL, Oracle), Latex.\\


%\resheading{\textbf{Relevant Courses Taken} }\\\\[\lsep]

%\indent Linear Algebra, Data Structures \& Algorithms, Object Oriented Programming, Probability \& Statistics,\\
%\indent Discrete Mathematics, Computer Networking, Operating Systems, Database Management Systems.\\
%\indent\textbf{MOOCs -- }Machine Learning (by Andrew Ng), Cryptography I (by Dan Boneh).\\


\resheading{\textbf{Honors \& Achievements}}\\[\lsep]\\[-0.2cm]

\begin{itemize}
\item {Secured 4\textsuperscript{th} position among 11,000 participants in the 4th CSI National Programming Contest 2017 organised by the Computer Society Of India.}\\[-0.5cm]
\item {Won 2\textsuperscript{nd} place in HelloWeb Hackathon 2016 hosted by the MozillaBBSR Club by designing a teaching kit to introduce kids to programming.}\\[-0.5cm]
%\item {Secured the highest grade "O" in Object Oriented Programming, Web Technology and Computer Networks as part of my B.Tech curriculum. }\\[-0.5cm]
\item {Secured a perfect score (100\%) in Mathematics in statewide Secondary Examination, 2013 among 1,020,000 students.}\\[-0.5cm]
\item {Awarded Chitroprobha Upadhi Certification by Bengal Music College, Kolkata, India in 2012 on completing a 6--year course on Painting.}\\[-0.5cm]
\item{Selected as one of 20 student judges from MP Birla group of schools for the cultural committee MP Birla Puja Utkarsh Samman 2014.}
\end{itemize}


\end{document}